Abstractions for Type-Level Programming

### 2022-04-19 article.tex
Do TODOs

The following \Cref{lem:inversion-of-subtyping} allows us to perform inversion on the subtyping relation,
which is important to show canonical forms (\Cref{lem:canonical-forms}) and inversion of typing (\Cref{lem:inversion-of-typing}).
Stating the lemma requires the definition of a new relation denoted $\Γ \⊢ \S \⇌ \T$, defined in \Cref{fig:harpoon}.
% TODO: clarify that harpoon is asymmetric (and so it disj)
It represents evidence of the mutual subtyping between a match type $\S$ and a type $\T$ with the additional constraint that this evidence was exclusively constructed using pairwise applications of \SMatch1/2, \SMatch3/4, and \STrans in both directions.
Intuitively, $\Γ \⊢ \S \⇌ \T$ is handier than two independent derivations of $\Γ \⊢ \S \<: \T$ and $\Γ \⊢ \T \<: \S$ because it allows simultaneous induction on both subtyping directions.
%
\input{proofs/inversion-of-subtyping.tex}
%
The first point of \Cref{lem:inversion-of-subtyping} uses the structure of the $\⇌$ to provide a form of inversion, which we use to prove each of the subsequent points.
In comparison with the corresponding inversion lemma in \Fsub's safety proof, the statement and the proof of \Cref{lem:inversion-of-subtyping} are longer and more intricate.
This difference is inevitable, given that match type reduction rules allow match expressions to be typed as the result of their reduction, which complexifies the inversion.

>>>>

The following \Cref{lem:inversion-of-subtyping} allows us to perform inversion on the subtyping relation,
which is important to show canonical forms (\Cref{lem:canonical-forms}) and inversion of typing (\Cref{lem:inversion-of-typing}).
Stating the lemma requires the definition of a new relation denoted $\Γ \⊢ \S \⇌ \T$, defined in \Cref{fig:harpoon}.
This relation represents evidence of the mutual subtyping between a match type $\S$ and a type $\T$ with the additional constraint that this evidence was exclusively constructed using pairwise applications of \SMatch1/2, \SMatch3/4, and \STrans in both directions.
Intuitively, $\Γ \⊢ \S \⇌ \T$ is handier than two independent derivations of $\Γ \⊢ \S \<: \T$ and $\Γ \⊢ \T \<: \S$ because it allows simultaneous induction on both subtyping directions.
Although $\Γ \⊢ \S \⇌ \T$ witness mutual subtyping between $\S$ and $\T$, that relation is asymmetric since its left-hand side is always a match type.
%
\input{proofs/inversion-of-subtyping.tex}
%
The first point of \Cref{lem:inversion-of-subtyping} uses the structure of the $\⇌$ to provide a form of inversion, which we use to prove each of the subsequent points.
In comparison with the corresponding inversion lemma in \Fsub's safety proof, the statement and the proof of \Cref{lem:inversion-of-subtyping} are longer and more intricate.
This difference is inevitable, given that match type reduction rules allow match expressions to be typed as the result of their reduction, which complexifies the inversion.

### 2022-04-19 preprint.tex
Do TODOs

When inferring the result type of a |dependent| method, our system lifts the method's body into a generalized singleton type.
This lifting will be precise for the subset of expressions that is representable in types, and approximative for the rest.
When we encounter an unsupported construct, we compute its type using the default mode, yielding a type |T| which we then integrate in the lifted body as |_: T|\footnotemark.
\footnotetext{%
When a generalized singleton type contains a component of form |_: T|, then that type is not singleton: it contains more than one value.
}

>>>>

When inferring the result type of a |dependent| method, our system lifts the method's body into a generalized singleton type.
This lifting will be precise for the subset of expressions that is representable in types, and approximative for the rest.
When we encounter an unsupported construct, we compute its type using the default mode, yielding a type |T| which we then integrate in the lifted body as |_: T|\footnotemark.
\footnotetext{%
When a generalized singleton type contains a component of form \texttt{(\_: T)}, then that type is not singleton: it might contains more than one value.}
